\section{Reports}
\label{sec:reports}

The bot can send to the controller reports containing \textit{current bot configuration}, \textit{scheduled attacks}, \textit{local system analysis} and \textit{local networks analysis}. Each section is attached to reports, if requested in configuration (see options \texttt{cnfInfo}, \texttt{tgtInfo}, \texttt{sysInfo} and \texttt{netInfo} in \ref{sec:configuration}). Since the first two sections are self-explanatory, we focus here only on local system and networks analysis.\\

The local system analysis includes the following components:
\begin{description}
  \setlength\itemsep{1em}
    \item [browsers] list of browsers installed on system. Browsers are detected by parsing the report of installed applications, returned by system's command of specific OS (e.g. Linux command: "\textit{dpkg -l}").
	\item [hostName] name associated with the host machine.
	\item [kernelVersion] version of the system kernel.
	\item [osArch] name of the system's architecture.
  	\item [osName] name of the operating system.
  	\item [osVersion] version of the operating system.
  	\item [userName] name of the active user on the host.
\end{description}
\;

An example of system analysis is the following:
\begin{verbatim}
{
  "Browsers" : "Google Chrome; Safari;",
  "HostName" : " MacBook Pro di Michele",
  "KernelVersion" : " Darwin 15.5.0",
  "OsArch" : "x86_64",
  "OsName" : "Mac OS X",
  "OsVersion" : "10.11.5",
  "UserName" : " Michele Porretta (micheleporretta)"
}
\end{verbatim}

The local networks analysis includes the following components:

\begin{description}
  \setlength\itemsep{1em}
  \item [Mac] Mac Address
  \item [Ip] Ip Address 
  \item [CurrentNetworkInfo] List of network interfaces with their details
  \item [NetworkStatistics] Statistics about network traffic, classified by protocol
\end{description}

An example of network analysis is the following:

\begin{verbatim}
{
  	"MAC" : "6C-D2-C4-76-FB-24",
  	"ip" : "10.224.219.219",
  	"currentNetworkInfo" : "[ network info ]",
  	"networkStatistics" : "[ statistics ]"
}
\end{verbatim}
